
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
in the begaining we recall the tidyvrese packages
read the file using read_csv
```{r}
activity <- read_csv("activity.csv",na =c("","NA"))
```
Histogram of the total number of steps taken each day
```{r}
hist(activity$steps,xlab = "day", ylab = "Step No.")
```
Mean and median number of steps taken each day
```{r} 
mean_seps <- mean(activity$steps, na.rm = TRUE)
median_steps_day <- median(activity$steps, na.rm = TRUE)
print(mean_seps)
print(median_steps_day)
```
Time series plot of the average number of steps taken
```{r}
library(zoo)
plot(zoo(activity$date,activity$steps),xlab = "Date",
     ylab = "Steps", main = "Time series of steps per days")
```
The 5-minute interval that, on average, contains the maximum number of steps
```{r}
activity[max(activity$interval, na.rm = TRUE),][[1]]
```

method No.1:-  code to describe and show a strategy for imputing missing data using mean
```{r}
activity$steps[is.na(activity$steps)] <- 
        mean(activity$steps, na.rm = TRUE)
```      
method No.2:-  code to describe and show a strategy for imputing missing data using medain
```{r}
activity$median_steps <- if_else(is.na(activity$steps) , 
        median(activity$steps,na.rm = T),activity$steps)
```
check the new data
```{r}
head(activity)
```
Histogram of the total number of steps taken each day after missing values are imputed
```{r}
hist(activity$steps, xlab = "Steps", ylab = "Freq"
     , main = "Total number of steps taken each day 
     after missing values are imputed")
```
Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
creat a column call week cantain weekday and weekend
```{r}
activity$week <- weekdays(activity$date)
activity$week <-as.factor(ifelse(activity$week == "Saturday"| 
                activity$week == "Sunday", "Weekend", "Weekday"))
```
creat the panel ploting using ggplot2
```{r}
ggplot(activity,aes(y = interval))+ geom_boxplot()+
        facet_wrap("week")
```
